Effects of Weather on Maize Yield in Kenya

### 2019-01-17 presentations/January2019/presentation1.tex
sllides presentation friday

\begin{itemize}
\item Tested by the Lagrange multipliear test developed by Baltagi \& Li ($1991$; $1995$)
\item[$\boldsymbol{\rightarrow}$] The error structure modelled as ARMA($1$,$1$) 
\begin{itemize}
\item The preferred error structure found using AIC
\end{itemize}
\end{itemize}

@@

\note{
First set of fixed effects found- stepwise like procedure. Then test of significant of random slopes
\vspace{0.3cm}to verify: alternative step-down model building approach
using the Satterthwaites method to determine the p-values of the individual t-tests

@@

\frametitle{Results}\label{Results} 
{\begin{threeparttable}
\caption{\normalsize{\textbf{ {Mixed  effects model:}} exponents of the coefficient estimates Log of maize yield and weather, ARMA(1,1) errors}}
%KEN11dK  KEN11dK_ASAL    KEN11dK_nonASAL										
\label{KenARe11_exponents} 
\setstretch{1.33}
\begin{tabular}{@{}lllllll} 
 \\
  \textbf{Fixed effects:}&\textit{\textbf{All counties}}&\textit{\textbf{ASAL}}&\textit{\textbf{non-ASAL}}\\
\vspace{-0.2cm}Intercept&$1.296^{***}$&$1.272^{*}$&$1.408^{**}$\\
 \vspace{-0.2cm}Prec. total&$1.081^{*}$&$1.007^{}$&$1.277^{***}$\\
  \vspace{-0.2cm}Prec. total sq.&$0.973^{*}$&$1.003$&$0.881^{***}$\\
 \vspace{-0.2cm}Prec. c. of var.&$0.924^{\bullet}$&$0.970$ &$0.907^{}$\\
 \vspace{-0.2cm}Dry spell -length\tnote{a}&$0.935^{*}$&$0.834^{**}$&$ 0.988^{}$\\
 \vspace{-0.2cm}Dry spells $\geq~4$ d.\tnote{b}&$0.939^{*}$&$0.855^{**}$&$0.989^{}$\\
 \vspace{-0.2cm}Temp. - average&$0.820^{***}$&$0.808^{*}$&$0.880$ $^{}$\\
 \vspace{-0.2cm}Temp. c. of var.&$1.043^{\bullet}$&$1.032$&$1.060$ ${*}$\\
  \hline
\textit{Number of observations:}  &\multicolumn{2}{l}{$1300$}&\multicolumn{2}{l}{$698$}&\multicolumn{2}{l}{$602$}
\\
\end{tabular} 
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets; \hfill $^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
            \begin{adjustwidth}{1cm}{} 
  \item[a] Length of the longest dry spell in number of days.
    \item[b] Number of dry spells lasting for four days or longer. 
     \end{adjustwidth}
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable}\par }
\end{frame}

>>>>

\begin{itemize}
\item Tested by the Lagrange multipliear test developed by Baltagi \& Li ($1991$; $1995$)
\end{itemize}
\color{darkblue}
\rotatebox[origin=c]{270}{\Huge{$\boldsymbol{	\rightsquigarrow}$}}
\color{black}
\\[2mm]The error structure modelled as ARMA($1$,$1$) 
\begin{itemize}
\item The preferred error structure found using the Likelihood Ratio statistics

@@

\note{
First set of fixed effects found- stepwise like procedure. Then test of significant of random slopes
\vspace{0.3cm}to verify: alternative step-down model building approach
using the Satterthwaites method to determine the p-values of the individual t-tests
\vspace{0.3cm} the error structure found as.. Likelihood ratio statistic. Comparison of AIC, BIC, loglik
}

@@

\frametitle{Mixed effects estimates:}\label{Results} 
{\begin{threeparttable}
\begin{footnotesize}
\caption*{Yield as dependent variable\hfill exponents of the coefficients: $\exp{\beta}$}
%KEN11dK  KEN11dK_ASAL    KEN11dK_nonASAL										
\label{KenARe11_exponents} 
\setstretch{1.33}
\begin{tabular}{llll} 
  \textbf{Fixed effects:}&\textit{\textbf{All counties}}&\textit{\textbf{ASAL}}&\textit{\textbf{non-ASAL}}\\
\vspace{-0.2cm}Intercept&$1.296^{***}$&$1.272^{*}$&$1.408^{**}$\\
 \vspace{-0.2cm}Prec. total&$1.081^{*}$&$1.007^{}$&$1.277^{***}$\\
  \vspace{-0.2cm}Prec. total sq.&$0.973^{*}$&$1.003$&$0.881^{***}$\\
 \vspace{-0.2cm}Prec. c. of var.&$0.924^{\bullet}$&$0.970$ &$0.907^{}$\\
 \vspace{-0.2cm}Dry spell -length in days&$0.935^{*}$&$0.834^{**}$&$ 0.988^{}$\\
 \vspace{-0.2cm}Dry spells $\geq~4$ days\tnote{b}&$0.939^{*}$&$0.855^{**}$&$0.989^{}$\\
 \vspace{-0.2cm}Temp. - average&$0.820^{***}$&$0.808^{*}$&$0.880$ $^{}$\\
 \vspace{-0.2cm}Temp. c. of var.&$1.043^{\bullet}$&$1.032$&$1.060$ ${*}$\\[2mm]
  \hline
\textit{Number of observations:}  &\multicolumn{1}{c}{$1300$}&\multicolumn{1}{c}{$698$}&\multicolumn{1}{c}{$602$}
\\
\end{tabular} 
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets; \hfill $^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
  \end{footnotesize}
\end{tablenotes}
\end{footnotesize}
  \end{threeparttable}\par }
\end{frame}
